### 2013-06-13 ms_V3.tex

\section*{Abstract}
Current global changes make it important to be able to predict which
interactions will occur in emerging ecosystems. Most of the current methods to
infer the existence of interactions between two species require a good
knowledge of their behaviour or a direct observation of interactions. In this paper, we
overcome these limitations by developing a method, inspired from the niche
model of food web structure, using the statistical relationship between predator and prey body size to infer the matrix of potential interactions among a pool of species. 
The novelty of our approach is to infer, for any species of a given species pool, the three species specific parameters of the niche model. It allows one to evaluate the feeding interactions of a new species entering the community. We find that this method gives robust predictions of the structure of
food webs, and that its efficiency is increased when the strength of the body-
size relationship between predators and preys increases. We finally illustrate the potential of the method to infer the metaweb structure of pelagic fishes of the Meditarrannean sea under different global change scenarios.
\newpage

@@

%------------------------------------------------------------
\subsection{Inferring parameters from the niche model and building the metaweb}
The niche model predicts the food web structure from a set of three species-specific parameters: the niche position $n_i$, the feeding niche optimum $c_i$ (called the centroid), and the feeding range $r_i$. A species $i$ will predate all species $j$ whose niche position $n_j$ lies within the interval $[c_i-r_i/2,c_i+r_i/2]$ (Fig. 1). We evaluate all of these parameters from the predator-prey body size relationship, enabling us to parameterize the metaweb from \emph{observed} interactions only. The parameterization is robust to the sampling effort, as it is much easier to document interactions than their absence \parencite{Martinez1999}. Our approach is however mostly limited to predatory interactions since the body size relationship between herbivores and primary producers is not as general \parencite{Riede2010}, and obviously do not hold for parasitic, mutualistic, or competitive networks.

Assuming that body size is the main niche axis structuring trophic interactions, the parameter $n_i$ corresponds simply to the log of body size (in mass or length) of species $i$. Though only the relative position of all species along the body size gradient needs to be respected, it is possible to standardize log body size values between 0 (minimum size in the regional species pool) and 1 (maximal size). We then consider a linear relationship between the decimal logarithm of body size and the centroid of the niche (the dark line at Fig. 1). This relationship is obtained by fitting the linear model $c = \mathrm{log}_{10}(B_{prey})=\alpha_0 + \alpha_1\times\mathrm{log}_{10}(B_{pred})$ to the data, where $B_{prey}$ and $B_{pred}$ are the prey and predator body size respectively. The lower and upper boundaries of the feeding range are easily obtained by fitting the 5\% and 95\% quantile regressions between $\mathrm{log}_{10}(B_{prey})$ and $\mathrm{log}_{10}(B_{pred})$ (the grey lines at Fig. 1, see the example at Fig. 2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.  In sum, the parameter $n_i$ for any species of the metaweb is given by the standardized value of the log body size $B_i$, $c_i$ is estimated from the linear regression between predator and prey log body size and $r_i$ from the quantile regressions.

>>>>

\section*{Abstract}

Current global changes make it important to be able to predict which
interactions will occur in emerging ecosystems. Most of the current methods to
infer the existence of interactions between two species require a good knowledge
of their behaviour or a direct observation of interactions. In this paper, we
overcome these limitations by developing a method, inspired from the niche model
of food web structure, using the statistical relationship between predator and
prey body size to infer the matrix of potential interactions among a pool of
species.  The novelty of our approach is to infer, for any species of a given
species pool, the three species specific parameters of the niche model. It
allows one to evaluate the feeding interactions of a new species entering the
community. We find that this method gives robust predictions of the structure of
food webs, and that its efficiency is increased when the strength of the body-
size relationship between predators and preys increases. We finally illustrate
the potential of the method to infer the metaweb structure of pelagic fishes of
the Meditarrannean sea under different global change scenarios.

\newpage

@@

%------------------------------------------------------------
\subsection{Inferring parameters from the niche model and building the metaweb}

The niche model predicts the food web structure from a set of three
species-specific parameters \parencite{Williams2000}: the niche position $n_i$, the feeding niche optimum
$c_i$ (called the centroid), and the feeding range $r_i$. A species $i$ will
predate all species $j$ whose niche position $n_j$ lies within the interval
$[c_i-r_i/2,c_i+r_i/2]$ (Fig. 1). We evaluate all of these parameters from the
predator-prey body size relationship, enabling us to parameterize the metaweb
from \emph{observed} interactions only. The parameterization is robust to the
sampling effort, as it is much easier to document interactions than their
absence \parencite{Martinez1999}. Our approach is however mostly limited to
predatory interactions since the body size relationship between herbivores and
primary producers is not as general \parencite{Riede2010}, and obviously do not
hold for parasitic, mutualistic, or competitive networks.

Assuming that body size is the main niche axis structuring trophic interactions,
the parameter $n_i$ corresponds simply to the log of body size (in mass or
length) of species $i$. Though only the relative position of all species along
the body size gradient needs to be respected, it is possible to standardize log
body size values between 0 (minimum size in the regional species pool) and 1
(maximal size). We then consider a linear relationship between the decimal
logarithm of body size and the centroid of the niche (the dark line at Fig. 1).
This relationship is obtained by fitting the linear model $c =
\mathrm{log}_{10}(B_{prey})=\alpha_0 +
\alpha_1\times\mathrm{log}_{10}(B_{pred})$ to the data, where $B_{prey}$ and
$B_{pred}$ are the prey and predator body size respectively. The lower and upper
boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
quantile regressions between $\mathrm{log}_{10}(B_{prey})$ and
$\mathrm{log}_{10}(B_{pred})$ (the dotted lines at Fig. 1, see the example at Fig.
2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.  In sum,
the parameter $n_i$ for any species of the metaweb is given by the standardized
value of the log body size $B_i$, $c_i$ is estimated from the linear regression
between predator and prey log body size and $r_i$ from the quantile regressions.
